\documentclass[11pt]{article}
\usepackage{graphicx} % Required to insert images
\usepackage{enumerate}
\usepackage{verbatim}
\usepackage{geometry}
\geometry{margin=1in, bottom=1in}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{pdfpages}
\usepackage{multicol}
\usepackage[colorlinks=true,linkcolor=blue,urlcolor=blue]{hyperref}
\usepackage{cite}
\usepackage{natbib}
\bibliographystyle{chicago}
\usepackage{indentfirst}
\usepackage{setspace}
\usepackage{float}
\usepackage{multirow}
\usepackage{enumitem}
\usepackage{bibentry}
\usepackage{sectsty}
\usepackage{helvet}


\renewcommand{\familydefault}{\sfdefault}

\title{CSDE 502: Responsible Conduct of Research\\ Final Essay Questions}
\author{Jessica Godwin}
\begin{document}
\maketitle

\begin{enumerate}
\item Pick a dataset from your area of research. It can be your own data, a commonly used dataset, data in a paper you've read, or data you are planning to collect. Use the FAIR and CARE principles of data management to assess the data and how it is used. Which FAIR and CARE principles are well considered and employed? Are there obvious ethical issues with the data and its use or how it's shared? 
\item Which topic covered in the course were most effective for you, i.e. was there a topic you had not thought deeply about before or you had not thought about as it pertains to your own area of research or was there a topic you developed a deeper or changed understanding of that you had previously thought about? Name the topic and describe how our readings and discussions were helpful to you.
\item Were there topics you anticipated or wished we would cover in this course that we did not? Were there topics you wish we had spent more or less time on? Name them and provide a bit of detail.
\end{enumerate}
\end{document}


